### 2023-06-25 main.tex
Added bibliography and fixed issue with unlocked images
Added the section conclusion. Removed redundancies in .bib file

\documentclass{article}
\usepackage{biblatex}
\usepackage{graphicx}
\addbibresource{prosem.bib}
\begin{document}
\section{Non-Linear Filters}
Non-linear filters serve as additional ways of filtering images. Linear filters can work exceptionally well for certain cases, however one will encounter scenarios where using Non-Linear filters will lead to a better result both visually (Image Processing) and performance-wise. One example noise removal, but more on that later. First of all it is important to look at what non-linear filters actually are.

@@

\begin{figure}[!hb]
    \centering
    \includegraphics[width=0.5\linewidth]{medianfiltering.jpeg}
    \caption{Figure 3.1}
    \label{fig:enter-label} 
\end{figure}
Now we have seen an example median filtering, compared to Gaussian filtering, for a specific scenario, and what it does, it is time to dive into what a \textit{median filter actually is}. The algorithm works in this way: Given an input signal, in this case an image, it goes through every single pixel of the image, and replaces the value with the median value of the adjacent pixels (See fig 3.2). One can also let it go through the image whilst checking adjacent pixels in a 3px, 10px, or generally X-pixel radius around the current one, and replace it with the median of the pixels inside this X-pixel radius. The "X-pixel radius" is called a kernel. Increasing the kernel-size of the filter might lead to a "smeared" and somewhat blurry look in many scenarios, as in Figure 3.3
\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{medianfiltering.PNG}
    \caption{Figure 3.2 - Illustration of how the mean filter algorithm works}
    \label{fig:enter-label}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{median_example.jpg}
    \caption{Figure 3.3}
    \label{fig:enter-label}
\end{figure}
However, even though median filters work relatively well for this specific scenario, the cure for cancer is yet to be found. There are (several) scenarios in which median filters might produce sub-optimal results.

@@

\subsubsection{Minimum- and Maximum Filtering}
Two more types of non-linear filters are minimum- and maximum filters. These two filters are often also called dilation and erosion filters, respectively. They are classified amongst the so called morphological filters. In many ways, the minimum and maximum filters are two sides of the same coin, they are very similar in all but one point. As the minimum filter moves along the image, processing as it should, it simply chooses the smallest value inside the current kernel and applies this value to the relevant pixel. Maximum filters work very similarly, but, as one might guess, they instead pick the largest value and assigns that to the relevant pixel. Given the two filters other names, dilation and erosion, it might not be too much of a leap to assume what an image processed by these filters would look like relative to the original. Minimum filters, or dilation filters, simply dilate the darker areas of images (since darker values tend to be assigned lower numbers). Effective if one wishes to thicken the borders of a dark-coloured letter on a light background in an image. Contrarily, the maximum filter, or erosion filter, will erode darker pixels from images. If a black pixel is surrounded by only white pixels, it will be gone after an erosion filter has been applied.
Lastly on minimum and maximum filters, a bit about binary images. What are binary images? They are in fact part of what led to the creation of morphological filters such as the here discussed minimum and maximum ones. As one might deduce from the name "binary images"  they operate with \textit{only} binary values. In other terms, each pixel can only have one of two values, black and white. Figure 3.6 demonstrates the application of the dilation and erosion filters on a binary image.
\begin{figure}[!hb]
    \centering
    \includegraphics[width=0.5\linewidth]{minmax1.png}
    \caption{Figure 3.5 illustrates the usage of minimum and maximum filters}
    \label{fig:enter-label}
\end{figure}

\begin{figure}[!hb]
    \centering
    \includegraphics[width=0.5\linewidth]{minmax2.PNG}
    \caption{Figure 3.6 using a minimum filter succeeded by a maximum filter fills the gaps in the figure and then decreases it's size}
    \label{fig:enter-label}
\end{figure}
\subsubsection{Mean Shift Filtering}
Placeholder text

@@

In essence, cellular automata are grids of cells, each containing what can be considered a finite state machine. They can be very useful in the analysis of many different systems, as well as in the fields of physics and biology. 
Now how specifically does one apply a cellular automaton to image processing?  As of now one of the most major application areas is noise removal in binary images.

@@

\subsection{Typical applications of Non-Linear filters}
The subject of where one can apply Non-Linear filters has already been touched upon. Likely, the most prominent application area of non-linear filters is in noise filtering.
\end{document}

>>>>

\documentclass{article}
\usepackage{biblatex}
\usepackage{graphicx}
\usepackage{float}
\addbibresource{prosem.bib}
\begin{document}
\section{Non-Linear Filters}
Non-linear filters serve as additional ways of filtering images. Linear filters can work exceptionally well for certain cases, however one will encounter scenarios where using Non-Linear filters will lead to a better result both visually (Image Processing) and performance-wise. One example noise removal, but more on that later. First of all it is important to look at what non-linear filters actually are.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\linewidth]{medianfiltering.jpeg}
    \caption{Figure 3.1}
    \label{fig:enter-label} 
\end{figure}
Now we have seen an example median filtering, compared to Gaussian filtering, for a specific scenario, and what it does, it is time to dive into what a \textit{median filter actually is}. The algorithm works in this way: Given an input signal, in this case an image, it goes through every single pixel of the image, and replaces the value with the median value of the adjacent pixels (See fig 3.2). One can also let it go through the image whilst checking adjacent pixels in a 3px, 10px, or generally X-pixel radius around the current one, and replace it with the median of the pixels inside this X-pixel radius. The "X-pixel radius" is called a kernel. Increasing the kernel-size of the filter might lead to a "smeared" and somewhat blurry look in many scenarios, as in Figure 3.3
\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{medianfiltering.PNG}
    \caption{Figure 3.2 - Illustration of how the mean filter algorithm works}
    \label{fig:enter-label}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{median_example.jpg}
    \caption{Figure 3.3}
    \label{fig:enter-label}
\end{figure}
However, even though median filters work relatively well for this specific scenario, the cure for cancer is yet to be found. There are (several) scenarios in which median filters might produce sub-optimal results.

@@

\subsubsection{Minimum- and Maximum Filtering}
Two more types of non-linear filters are minimum- and maximum filters. These two filters are often also called dilation and erosion filters, respectively. They are classified amongst the so called morphological filters. In many ways, the minimum and maximum filters are two sides of the same coin, they are very similar in all but one point. As the minimum filter moves along the image, processing as it should, it simply chooses the smallest value inside the current kernel and applies this value to the relevant pixel. Maximum filters work very similarly, but, as one might guess, they instead pick the largest value and assigns that to the relevant pixel. Given the two filters other names, dilation and erosion, it might not be too much of a leap to assume what an image processed by these filters would look like relative to the original. Minimum filters, or dilation filters, simply dilate the darker areas of images (since darker values tend to be assigned lower numbers). Effective if one wishes to thicken the borders of a dark-coloured letter on a light background in an image. Contrarily, the maximum filter, or erosion filter, will erode darker pixels from images. If a black pixel is surrounded by only white pixels, it will be gone after an erosion filter has been applied.
Lastly on minimum and maximum filters, a bit about binary images. What are binary images? They are in fact part of what led to the creation of morphological filters such as the here discussed minimum and maximum ones. As one might deduce from the name "binary images"  they operate with \textit{only} binary values. In other terms, each pixel can only have one of two values, black and white. Figure 3.6 demonstrates the application of the dilation and erosion filters on a binary image.
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\linewidth]{minmax1.png}
    \caption{Figure 3.5 illustrates the usage of minimum and maximum filters}
    \label{fig:enter-label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\linewidth]{minmax2.PNG}
    \caption{Figure 3.6 using a minimum filter succeeded by a maximum filter fills the gaps in the figure and then decreases it's size}
    \label{fig:enter-label}
\end{figure}
\subsubsection{Mean Shift Algorithm}
The mean shift algorithm is often referred to as a "hill climbing algorithm". Given for instance a scatter plot, or such, the mean shift algorithm will locate the area of the plot where the data-point density is at it's highest, metaphorically speaking, a hill (densest data cluster).

@@

In essence, cellular automata are grids of cells, each containing what can be considered a finite state machine. They can be very useful in the analysis of many different systems, as well as in the fields of physics and biology. 
Now how specifically does one apply a cellular automaton to image processing?  As of now one of the most major application areas is noise removal in binary images. \cite{inproceedings} As demonstrated by Rosin and Sun\cite{rosin} it can also be used for edge detection, which, as previously mentioned, is an \textit{essential} part of image processing.

@@

\subsection{Typical applications of Non-Linear filters}
The subject of where one can apply Non-Linear filters has already been touched upon. Likely, the most prominent application area of non-linear filters is in noise filtering.

\subsection{Conclusion}
Now that we have discussed some different image processing algorithms, specifically several linear and non-linear filtering ones it is time to assess their use cases, and to compare them. A first obvious question that may arise is whether any specific type of filtering is simply objectively better. As with many situations in life, and different fields of computer science, this is hard to find. Just as it may be hard to determine a specific sorting algorithm as objectively the best in any given scenario, it is equally hard to determine an objectively best filtering algorithm. In some programs or prototypes it may be prudent to apply a simple filtering algorithm as nothing too extensive is needed. For ease of use and understanding, many linear filters may well hold the edge over most non-linear filters. Many non-linear filters can seem less intuitive, and hence be harder to understand and implement, possibly being overly complex for certain scenarios. It is also important to note that in most use cases, be that in pure image processing, signal processing or computer vision, many filters are used in combination to achieve optimal results. Applying specific filtering techniques for specific scenarios and then weaving all the data they produce together may well produce far more accurate data than taking a "one-size fits all" approach to filters.

Filtering can be an incredibly helpful tool in processing images. Removing noise from images, increasing clarity, detecting edges and such have applications in the closely related field of computer vision as well, but none of this comes without it's drawbacks. As we have seen, applying a wrong filter can easily lead to a decrease in clarity of images, perhaps only succeeding in making an image more blurry. Moreover, even if applying "the optimal" filtering algorithm it by no stretch of the imagination guarantees a completely noise and error free result. Filtering is not magic, certain images may be past a point in which it physically cannot get any clearer. This also leads into another issue, namely over-processing. Passing a signal or an image through a filter one time (or more) too many can lead to results which no longer resemble the original, what it was supposed too look like, or lead to unnatural results. In these cases, one may very well consider whether the application of a filter actually helped. If one in certain scenarios realizes that this answer for this case was actually no, one may already have spent far too many resources and hours on something that ended up being producing nothing practical. Resource management is very often of the essence.

Even with all the potential drawbacks that filtering can bring, the pros most likely heavily outweigh the cons. As technology advances, new techniques and new equipment will lead to even more advanced image processing. With the advent of AI, many of it's techniques may be appended to already existing techniques, or spawn new ones entirely. This will all surely lead to even more advanced filtering techniques, and with the blistering increase of data (big data) out there, there is no lack in training data for all AI/ML/Neural Network's needs. This will probably be the most major source of improvement for future filtering techniques.

\printbibliography

\end{document}
